### 2017-09-27 TF-vldb2018/sec-tsimAlg.tex

\revise{
\stitle{Algorithm \grouprec.} As shown in Fig.~\ref{alg-grouprec}, it takes input as $P$, $G$, and two integers $r$ and $k$, and outputs the top-$k$ densest perfect subgraphs in $G$ for $P$.
It firstly checks whether $P$ is satisfiable (line 1). 
If so, for each ball $\ball{[v,r]}$ in $G$, it computes the maximum core $\ball{}_{C}$ of $\ball{[v,r]}$, and checks whether the early termination condition holds (lines 3-6).
If so, it returns the current top-$k$ densest perfect subgraphs as top-$k$ teams;
otherwise, it computes the perfect subgraph $G_{s}$ of $P$ in $\ball{[v,r]}$ via team simulation by invoking \rgraphsim (line 7, see Appendix),
an adaption from graph simulation~\cite{infsimu95,FanLMTWW10} and checking capacity bounds (line 8).
It then computes perfect subgraphs $G'_{s}$ of $P$ in inner balls $\ball{[v,t]}$ by invoking \incsim, an extension of the incremental algorithm in \cite{FanWW13-tods} and checking capacity bounds (lines 9-11, see Appendix).}
%Procedure \rgraphsim is deferred to the appendix, which is an adaption from graph simulation~\cite{infsimu95,FanLMTWW10}.}
%by extending from directed to undirected graphs,  incorporating the capacity constraint check, and only maintaining the capacity bounds satisfied perfect subgraphs.

>>>>

\revise{
\stitle{Algorithm \grouprec.} As shown in Fig.~\ref{alg-grouprec}, it takes input as $P$, $G$, and two integers $r$ and $k$, and outputs the top-$k$ densest perfect subgraphs in $G$ for $P$.
It firstly checks whether $P$ is satisfiable (line 1). 
If so, for each ball $\ball{[v,r]}$ in $G$, it computes the maximum core $\ball{}_{C}$ of $\ball{[v,r]}$, and checks whether the early termination condition holds (lines 3-6).
If so, it returns the current top-$k$ densest perfect subgraphs as top-$k$ teams;
otherwise, it computes the perfect subgraph $G_{s}$ of $P$ in $\ball{[v,r]}$ via team simulation by invoking \rgraphsim (line 7, see full version~\cite{fullvldb18}),
an adaption from graph simulation~\cite{infsimu95,FanLMTWW10} and checking capacity bounds (line 8).
It then computes perfect subgraphs $G'_{s}$ of $P$ in inner balls $\ball{[v,t]}$ by invoking \incsim, an extension of the incremental algorithm in \cite{FanWW13-tods} and checking capacity bounds (lines 9-11, see~\cite{fullvldb18}).}
%Procedure \rgraphsim is deferred to the appendix, which is an adaption from graph simulation~\cite{infsimu95,FanLMTWW10}.}
%by extending from directed to undirected graphs,  incorporating the capacity constraint check, and only maintaining the capacity bounds satisfied perfect subgraphs.

### 2017-09-27 TF-vldb2018/subsec-Ginc.tex

\eat{
\proofS
The proof is similar to the one of Proposition~\ref{prop-canaffballs}.
\identifyaffball filters out the balls that cannot match all fragments,
and there are no data updates on the ball.
\eop}

The proof is deferred to Appendix.

@@

\stitle{Correctness \& complexity analyses}. The correctness of \incd \wrt $\Delta G$ follows from Proposition~\ref{prop-affected-datainc} and the correctness of \incmatch and \comb.
\incd is overall in
$O(\bigcup_{\widehat{G\oplus\Delta G}\in \affballsx}\bigcup_{i\in[1,h]}$ $r|M(P_{fi}, \widehat{G\oplus\Delta G})|$+$r|P||\affballsx|)$ time \wrt $\Delta G$, while $r$ is small, \ie 2 or 3  (See Appendix).
\looseness=-1

>>>>

The proof is deferred to the full version~\cite{fullvldb18}.

@@

\stitle{Correctness \& complexity analyses}. The correctness of \incd \wrt $\Delta G$ follows from Proposition~\ref{prop-affected-datainc} and the correctness of \incmatch and \comb.
\incd is overall in
$O(\bigcup_{\widehat{G\oplus\Delta G}\in \affballsx}\bigcup_{i\in[1,h]}$ $r|M(P_{fi}, \widehat{G\oplus\Delta G})|$+$r|P||\affballsx|)$ time \wrt $\Delta G$, while $r$ is small, \ie 2 or 3  (See~\cite{fullvldb18}).
\looseness=-1

### 2017-09-27 TF-vldb2018/subsec-Qinc.tex

The proof is deferred to Appendix.

@@

\stitle{Correctness \& complexity analysis}.
The correctness of \incp is assured by the correctness of \identifyaffball (Proposition~\ref{prop-canaffballs}), \incmatch, \comb, and early return property (Lemma~\ref{lemma-approximation-bound}).
\incp is in $O(\bigcup_{\hat{G}\in \affballsx}\bigcup_{i\in[1,h]}(|M(P_{fi}, \hat{G})|$ + $r|M(P_{fi} \oplus \Delta P_{fi}, \hat{G})|$) + $r|P \oplus \Delta P||\affballsx|$+$|\Delta P|)$ time \wrt $\Delta P$, while $r$ is small, \ie 2 or 3 (See Appendix).

>>>>

The proof is deferred to the full version~\cite{fullvldb18}.

@@

\stitle{Correctness \& complexity analysis}.
The correctness of \incp is assured by the correctness of \identifyaffball (Proposition~\ref{prop-canaffballs}), \incmatch, \comb, and early return property (Lemma~\ref{lemma-approximation-bound}).
\incp is in $O(\bigcup_{\hat{G}\in \affballsx}\bigcup_{i\in[1,h]}(|M(P_{fi}, \hat{G})|$ + $r|M(P_{fi} \oplus \Delta P_{fi}, \hat{G})|$) + $r|P \oplus \Delta P||\affballsx|$+$|\Delta P|)$ time \wrt $\Delta P$, while $r$ is small, \ie 2 or 3 (See full version~\cite{fullvldb18}).
